Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-07-19 SIR_manuscript.tex
breaking the sections, filling the BMB template

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}
\usepackage{authblk}

@@

% https://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage{xspace}

@@

%% DE: table stuff
\renewcommand{\arraystretch}{1.5} % more interline spacing
%% https://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
\usepackage{ragged2e}
\usepackage{array} % for m{...}

@@

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model}
\author[1]{Ali Gharouni}
\author[1]{F.M. Abdelmalek}
\author[1,3,5]{David J. D. Earn}
\author[2,4,3]{Jonathan Dushoff}
\author[1,2,3]{Benjamin M. Bolker}

\affil[1]{Department of Mathematics \& Statistics, McMaster University, Hamilton, Canada}
\affil[2]{Department of Biology, McMaster University, Hamilton, Canada}
\affil[3]{Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada}
\affil[4]{South African Centre for Epidemiological Modelling and Analysis, University of Stellenbosch, Stellenbosch, South Africa}

@@

\begin{figure}
\begin{center} 
\includegraphics[scale=1.5]{pix/sir_comp.pdf}
\caption{\small Flowchart of the SIR (Susceptible-Infectious-Recovered) model, \ref{model}. The disease-based status of a compartment $X$ ($X \in \{S,I,R\}$) is combined with the testing status including $X\_u$, $X\_p$, $X\_n$ and $X\_c$, for \emph{untested}, waiting-for-\emph{positive}, waiting-for-\emph{negative}, or \emph{confirmed positive}, respectively. The force of infection is denoted by $\Lambda$ (Eq.~\eqref{Lambda}); $\gamma$ is the recovery rate; $\omega$ is the rate of test return; and \testing{X} (Eq. \eqref{test}) and $p_X$ represent the \percap testing rate and the sensitivity (probability of positive tests), respectively, for compartment $X$. For further description of the parameters see \cref{tab:params}.
Note that there is a slight mismatch in the top-to-bottom order of the testing-based compartments of each disease-based compartment $X$ between this flowchart and the model equations \eqref{model}; here we have switched  $X\_u$ and $X\_n$ for visual clarity.
\label{fig:flowchart}}
\end{center} 
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}
\usepackage{authblk}
\usepackage{ragged2e}
\usepackage{array}

@@

% https://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

%% DE: table stuff
\renewcommand{\arraystretch}{1.5} % more interline spacing
%% https://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
% \usepackage{ragged2e}
% \usepackage{array} % for m{...}

@@

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model}
\author[1]{Ali Gharouni}
\author[1]{F.M. Abdelmalek}
\author[1,3]{David J. D. Earn}
\author[2,3,4]{Jonathan Dushoff}
\author[1,2,3]{Benjamin M. Bolker}

\affil[1]{Department of Mathematics and Statistics, McMaster University, Hamilton, Canada}
\affil[2]{Department of Biology, McMaster University, Hamilton, Canada}
\affil[3]{Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada}
\affil[4]{South African Centre for Epidemiological Modelling and Analysis, University of Stellenbosch, Stellenbosch, South Africa}

@@

\begin{figure}
\begin{center} 
\includegraphics[scale=1.5]{pix/sir_comp.pdf}
\caption{\small Flowchart of the SIR (Susceptible-Infectious-Recovered) model, \ref{model}. The disease-based status of a compartment $X$ ($X \in \{S,I,R\}$) is combined with the testing status including $X\_u$, $X\_p$, $X\_n$ and $X\_c$, for \emph{untested}, waiting-for-\emph{positive}, waiting-for-\emph{negative}, or \emph{confirmed positive}, respectively. The force of infection is denoted by $\Lambda$ (Eq.~\eqref{Lambda}); $\gamma$ is the recovery rate; $\omega$ is the rate of test return; and \testing{X} (Eq. \eqref{test}) and $p_X$ represent the \percap testing rate and the sensitivity (probability of positive tests), respectively, for compartment $X$. For further description of the parameters see Table~ \ref{tab:params}.
Note that there is a slight mismatch in the top-to-bottom order of the testing-based compartments of each disease-based compartment $X$ between this flowchart and the model equations \eqref{model}; here we have switched  $X\_u$ and $X\_n$ for visual clarity.
\label{fig:flowchart}}
\end{center} 
\end{figure}
